---
title: BFI's 100 Greatest Movies
author: Martin Moench
date: '2020-04-06'
slug: bfi-s-100-greatest-movies
categories:
  - movies
tags:
  - 100 greatest movies
  - greatest movies
  - movies
  - bfi
  - sight & sound
  - '100'
  - all time
  - list
  - download
  - notion
  - notion.so
  - google sheets
  - sheets
  - picker
  - random
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
bfi100 <- readRDS("/cloud/project/public/post/2020-04-06-bfi-s-100-greatest-movies_files/bfi100.rds")
```

In 2012, the **British Film Institute (BFI)** published a list of what are deemed to be the [100 Greatest Movies of All Time](https://www.bfi.org.uk/greatest-films-all-time) according to movie critics. The opinion polls were conducted by BFI's **Sight & Sound** magazine and included more than 800 critics, programmers, academics, and distributors from all over the world.

You can see the list below. Please note, I assigned a rank from 1 to 100 (well, there actually seem to be 101 entries in this list `r emo::ji("thinking")``r emo::ji("man_shrugging")`), which is slightly different to the original list where multiple movies can share the same rank.

If you are like me and like to work your way through lists (especially during times of Coronavirus lockdown) then I hope you will find the below useful. I couldn't find an easily downloadable or forkable version of the **BFI's 100 Greatest Film** list, so I created a couple of solutions (Notion.so / Google Sheets). I also included a little feature that will return a randomly selected movie from the list (just in case you ever face good old choice paralysis).

<div style="text-align: center;">
  <a href='https://www.notion.so/BFI-s-100-Greatest-Movies-041d62b439d4418d9a017a7dba40c21c' style = "background-color: #1c87c9;
         border: none;
         color: white;
         padding: 10px 14px;
         text-align: center;
         text-decoration: none;
         display: inline-block;
         font-size: 17px;
         margin: 4px 2px;
         cursor: pointer;" target = "_blank">Notion.so (View / Duplicate)</a>
  <a href = 'https://docs.google.com/spreadsheets/d/1WB9ypPGtRasp0wH4TvsA526qG1Efw9R0MmBfgKv93fY/edit?usp=sharing' style = "background-color: #1c87c9;
         border: none;
         color: white;
         padding: 10px 14px;
         text-align: center;
         text-decoration: none;
         display: inline-block;
         font-size: 17px;
         margin: 4px 2px;
         cursor: pointer;" target='_blank'>Google Sheets</a>
</div>

### Why not watch:

<div style = "text-align: center;">
  <iframe src="https://mmoench.shinyapps.io/movie-picker/" style="max-height:100px; outline: none; border: none; padding-bottom: -25px;margin-bottom: -25px;"></iframe>
</div>

### BFI’s 100 Greatest Films:

```{r, echo=FALSE, message=FALSE}
# library(dplyr)
# 
# bfi100 <- readRDS("/cloud/project/public/post/2020-04-06-bfi-s-100-greatest-movies_files/bfi100.rds")

bfi100 %>% 
  mutate(title = paste0("<a href='",wiki_link,"'target='_blank'>",title,"</a>")) %>%
  select(-ranking, -wiki_link) %>% 
  DT::datatable(escape = F, options = list(scrollX = TRUE, scrollCollapse = TRUE))
```

